---
title: "Teto Remuneratório (PL 6726/2016)"
output:
  html_document:
    df_print: paged
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(vistime)
library(tidyverse)
library(rcongresso)
data <- read_csv("../data/vis/tramitacao/data-camara.csv") %>% unique()

tramita_id <- fetch_id_proposicao(tipo = "PL", ano = "2016", numero = "6726")
proposicao <- fetch_proposicao(id = tramita_id)
tramitacao <- read_csv("../data/camara/tramitacao_camara_2121442.csv")
```

##### Nome da Proposição: `r toString(proposicao$siglaTipo)` `r toString(proposicao$numero)`/`r toString(proposicao$ano)`
##### Tipo da Proposição: `r toString(proposicao$descricaoTipo)`
##### Regime: `r toString(proposicao$statusProposicao.regime)`
##### Atual status: `r toString(proposicao$statusProposicao.descricaoTramitacao)`
##### Emenda: `r toString(proposicao$ementa)`

```{r echo=FALSE}
vistime(data, events="label", groups="group", title="Fases da tramitação", colors = "color", showLabels=FALSE)
```

#### Eventos que ocorrem durante a tramitação

```{r echo=FALSE}
tramitacao %>% select(evento) %>% group_by(evento) %>% 
  filter(!is.na(evento)) %>% summarise(frequência = n()) %>% 
  arrange(-frequência)
```

